\newpage

\section{Epilog}

\subsection{Stability and security considerations}

Since the \product{dyncall} library doesn't know anything about the called function itself
(except its address), no parameter-type validation is done. Thus in order to avoid crashes, data corruption, etc., the user is urged to ascertain the number and types of parameters. 
It is strongly advised to double check the parameter types of every function to be called, and not to call unknown functions at all.\\

Consider a simple program that issues a call by directly passing some command line arguments to the call itself, or even worse, by indirectly choosing a library and a function to call. Such unchecked input data can be quite easily used to intentionally crash the program , or to hijack it and take control of the program flow.\\
To put it in a nutshell, if not used with care, programs depending on the \product{dyncall}
and the dynload library, can become arbitrary function call dispatchers by
manipulating their input data. Successful exploits of programs like the one
outlined above can be misused as very powerful tools for a wide variety of
malicious attacks, \ldots
 

\subsection{Multi-threading}

The \product{dyncall} library is thread-safe and reentrant, by means that it
works correctly during execution of multiple threads if, and only if there is
at most a single thread pushing arguments to a CallVM (invoking the call is
always thread-safe, though). However, since there's no limitation on the
number of created CallVM objects, it is advised to keep a copy for each
thread.


\subsection{Supported types}

Currently, the \product{dyncall} library supports all of ANSI C's integer,
floating point and pointer types as function call arguments as well as return
values. Additionally, C++'s \capi{bool} type is supported. Due to the still
rare and often incomplete support of the \capi{long double} type on various
platforms, the latter is currently not supported.


\subsection{Roadmap}

The \product{dyncall} library should be extended by a wide variety of other
calling conventions and ported to other, more esoteric platforms. With its low
memory footprint it surely might come in handy on embedded systems, which are,
with the exception of the ARM9E family of processors, currently unsupported.
Furthermore, the authors plan to write some more scripting language bindings,
examples, and other projects that are based on it.\\
Besides \product{dyncall} the dynload library needs to be extended with
.dylib, .so and other shared library format support (e.g. AmigaOS .library or
GEM \cite{.ldg} files).

